*Supplement* Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary

### 2024-02-09 manu-draft.qmd
ESCO submitted

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      orcid: 0000-0002-4996-0059
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      orcid: 0000-0002-6032-0570
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      orcid: 0000-0003-3220-3737
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      orcid: 0000-0002-3847-6501      
      institute: [TBEP]
      correspondence: false
  - Bradley T Furman:
      email: Bradley.Furman@myfwc.com
      orcid: 0000-0002-9284-8388
      institute: [FWRI]
      correspondence: false
  - David J Karlen: 
      email: karlen@epchc.org
      orcid: 0000-0002-1432-9099
      institute: [EPCHC]
      correspondence: false
  - Christopher Pratt: 
      email: prattc@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Christopher J Anastasiou: 
      email: chris.anastasiou@swfwmd.state.fl.us
      institute: [SWFWMD]
      correspondence: false      
  - Edward T Sherwood:
      email: esherwood@tbep.org
      orcid: 0000-0001-5330-302X
      institute: [TBEP]
      correspondence: false

@@

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
crossref: 
  fig-title: Fig.
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      orcid: 0000-0002-4996-0059
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      orcid: 0000-0002-6032-0570
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      orcid: 0000-0003-3220-3737
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      orcid: 0000-0002-3847-6501      
      institute: [TBEP]
      correspondence: false
  - Bradley T Furman:
      email: Bradley.Furman@myfwc.com
      orcid: 0000-0002-9284-8388
      institute: [FWRI]
      correspondence: false
  - David J Karlen: 
      email: karlen@epchc.org
      orcid: 0000-0002-1432-9099
      institute: [EPCHC]
      correspondence: false
  - Christopher Pratt: 
      email: prattc@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Christopher J Anastasiou: 
      email: chris.anastasiou@swfwmd.state.fl.us
      institute: [SWFWMD]
      correspondence: false      
  - Edward T Sherwood:
      email: esherwood@tbep.org
      orcid: 0000-0001-5330-302X
      institute: [TBEP]
      correspondence: false

@@

*Key words*: climate change; seagrass; salinity; temperature; Tampa Bay

## Statements and Declarations {.unnumbered}

The authors have no competing interests to declare that are relevant to the content of this article.

### 2024-02-09 supplement.qmd
ESCO submitted

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "*Supplement* Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      correspondence: false
  - Bradley T Furman:
      email: Bradley.Furman@myfwc.com
      institute: [FWRI]
      correspondence: false
  - David J Karlen: 
      email: karlen@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Christopher Pratt: 
      email: prattc@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Christopher J Anastasiou: 
      email: chris.anastasiou@swfwmd.state.fl.us
      institute: [SWFWMD]
      correspondence: false    
  - Edward T Sherwood:
      email: esherwood@tbep.org
      institute: [TBEP]
      correspondence: false

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "*Supplement* Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
crossref: 
  fig-title: Fig.
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      correspondence: false
  - Bradley T Furman:
      email: Bradley.Furman@myfwc.com
      institute: [FWRI]
      correspondence: false
  - David J Karlen: 
      email: karlen@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Christopher Pratt: 
      email: prattc@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Christopher J Anastasiou: 
      email: chris.anastasiou@swfwmd.state.fl.us
      institute: [SWFWMD]
      correspondence: false    
  - Edward T Sherwood:
      email: esherwood@tbep.org
      institute: [TBEP]
      correspondence: false
